MINOS Handover Plots

### 2023-03-01 minos/validation/handovers.Rmd
Small path changes to existing scripts, and added a notebook for investigating interventions

```{r}
source('R_Scripts/utils.r')
```

@@

# baseline path and output subdirectory
base.path <- 'Minos/output/default_config/baseline/'
base.path <- get_runtime_subdirectory(base.path)

base.files <- list.files(base.path, 
                         pattern = '[0-9]{4}.csv',
                         full.names = TRUE)
base.dat <- do.call(rbind, lapply(base.files, read.csv))
```

>>>>

```{r}
source('Minos/minos/validation/utils.r')
```

@@

out.path <- 'Minos/output/default_config/'
base.dat <- read_output(out.path, 'baseline')
```
